---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# MA429 Final Project

This repository is for the submission of the MA429 Final Project for Group 1.

## Project Outline & Deadlines

```{r, echo=FALSE}
library(kableExtra)
library(knitr)

outline = data.frame(
  Items = c("Introduction", "Description of Dataset", "Literature Review", "Data Load/Conversion", "Descriptive Statistics", "Dimensionality Reduction (PCA & t-SNE)", "Performance Metrics", "Algorithms", "   Neural Network", "   Logistic regression", "   Random Forest", "XGBoost", "   Model Ensembles", "Limitations", "Conclusion"),
  Person = c("Philipp", "Philipp", "Philipp", "Jin", "Ruaridh", "Philipp", "Jin", "", "Philipp", "Jin", "Jin", "Ruaridh", "All", "Jin", "Philipp"),
  Deadline = c("14/04", "04/04", "04/04", "27/03", "04/04", "04/04", "04/04", "", "11/04", "11/04", "11/04", "14/04", "14/04", "14/04", "14/04")
)

kable(outline)
```

## Report Plan

### Executive Summary

- One page to summarise problem setting and main conclusions
- No technical details

### Main

#### Introduction (Philipp)

- Outline report structure
- Brief overview of dataset and methods (no details).
- Review of existing literature
- What are we doing differently?
- Project objectives

#### Data Understanding

- Explain literature data transformations in detail (Philipp)
- Exploratory analysis incl. visuals (Ruaridh)
- Time series metrics and possible additional features (Ruaridh)

#### Data Preparation

- PCA vs t-SNE incl. visuals (Philipp)
- Overview of dataset transformation (Ruaridh)

#### Modelling

- Explain performance metrics (Jin)
- Outline all models chosen (All)
- Explain methods not covered in MA429 (Ruaridh - XGBoost; Philipp - RNN if included)
- Justify hyperparameters chosen for calibration and otherwise (All)

#### Evaluation

- Compare performance of models across all datasets (Philipp)
- Graphical summary of performance metrics. (Ruaridh)
- Pros and cons of each model choice and dataset choice (Jin)
- Practical consequences, impacts, surprising/interesting discoveries (Ruaridh)
- Overall conclusion and further work (Philipp)
